### 2017-05-22 2017mergingmerges/section/03-Definition.tex
Say that injection is a meta-level operation

Execution of a network is non-deterministic. At any moment several processes may be able to take a step, while others are blocked. As with Kahn processes~\cite{kahn1976coroutines}, pulling from a channel is blocking. This enables the overall sequence of values on each output channel to be deterministic. Unlike Kahn processes, pushing to a channel can also block. Each consumer has a single element buffer, and pushing only succeeds when that buffer is empty.

@@

Each channel may be pushed to by a single process only, so in a sense each output channel is owned by a single process. The only intra-process communication is via channels and streams. Our model is ``pure data flow'' as there are no side-channels between processes. This is in contrast to systems such as StreamIt~\cite{thies2002streamit}, where processes can communicate via asynchronous messages as well as channels.

% -----------------------------------------------------------------------------
\subsubsection{Injection}
Figure~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. The statement $(\ProcInject{p}{v}{c}{p'})$ reads ``given process $p$, injecting value $v$ into channel $c$ yields an updated process $p'$''. The @injects@ form is similar, operating on a process network.

@@

% -----------------------------------------------------------------------------
\subsubsection{Advancing}
Figure~\ref{fig:Process:Eval:Shake} gives the rules for advancing a single process. The first set of rules handle specific instructions. The statement $(\ProcBlockShake{i}{is}{bs}{a}{l}{is'}{us'})$ reads ``instruction $i$, given channel states $is$ and the heap bindings $bs$, passes control to instruction at label $l$ and yields new channel states $is'$, heap update expressions $us'$, and performs an output action $a$.'' An output action $a$ is an optional message of the form $(\Push~\Chan~\Value)$, which encodes the value a process pushes to one of its output channels. We write ~$\cdot$~ for an empty action.

>>>>

Execution of a network is non-deterministic. At any moment several processes may be able to take a step, while others are blocked. As with Kahn processes~\cite{kahn1976coroutines}, pulling from a channel is blocking, which enables the overall sequence of values on each output channel to be deterministic. Unlike Kahn processes, pushing to a channel can also block. Each consumer has a single element buffer, and pushing only succeeds when that buffer is empty.

@@

Each channel may be pushed to by a single process only, so in a sense each output channel is owned by a single process. The only intra-process communication is via channels and streams. Our model is ``pure data flow'' as there are no side-channels between processes --- in contrast to ``impure data flow'' systems such as StreamIt~\cite{thies2002streamit}.

% -----------------------------------------------------------------------------
\subsubsection{Injection}
Figure~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. Injection is a meta-level operation, in contrast to @pull@ and @push@ which are instructions in the object language. The statement $(\ProcInject{p}{v}{c}{p'})$ reads ``given process $p$, injecting value $v$ into channel $c$ yields an updated process $p'$''. The @injects@ form is similar, operating on a process network.

@@

% -----------------------------------------------------------------------------
\subsubsection{Advancing}
Figure~\ref{fig:Process:Eval:Shake} gives the rules for advancing a single process. The statement $(\ProcBlockShake{i}{is}{bs}{a}{l}{is'}{us'})$ reads ``instruction $i$, given channel states $is$ and the heap bindings $bs$, passes control to instruction at label $l$ and yields new channel states $is'$, heap update expressions $us'$, and performs an output action $a$.'' An output action $a$ is an optional message of the form $(\Push~\Chan~\Value)$, which encodes the value a process pushes to one of its output channels. We write ~$\cdot$~ for an empty action.
